\chapter{\abstractname}
% Looking closer at biological processes will often reveal interesting mechanisms. They most often evolved over time and helped the organism evoling them to survive by having a little edge on their contrahents. Trying to understand them and copying them already lead to great achiev



In this thesis the capabilities of Spiking Neural Networks for the use in robotics is studied. The aim is to realize a controller for a snake-like robot with a slithering movement gait. To sense its environment the robot is equipped with a Dynamic Vision Sensor. This is an optical sensor which has very high temporal resolution and needs far less data volume to work as it doesn't send frames at a fixed rate but events if a significant change in a pixel occurs. The events sent form the camera can be converted to input spikes for the network with almost no overhead. The combination of these technologies is promising for the use in autonomous platforms as both have a lower energy consumption than comparable solutions. Additionally spiking neural networks work continous in time which enables a smaller latency for the robot and it can react faster on a changing situation. The snake robot has very versatile movement capabilities which makes the concept interesting especially for difficult terrain.
\newline
In this setup movement of the snakes head while slithering is a special challenge as the sensor input changes throughout the movement. Thus the first aim in this thesis is to set up a simple spiking neural network to control the robot in an object following task. The next aim is to evolve the control model and enable the network to control the head independent from the movement direction. The capabilities of controlling this more complex setup are tested for different single and multilayer network topologies. The networks use reward modulated STDP synapses and reward backpropagation is used for multilayer networks.
The results show that the simplest network is capable to precisely control the snake to follow a target. In the more complex control task on the other hand, no single layered network was able to follow the target.
Only multilayered networks were able to succeed in the task when having to control the head and the movement direction of the robot.

%This was only achieved by a multilayered network which had a similar performance to the single layered network in the more simple setup



%TODO: Abstract


